### 2020-11-07 Thesis-Chapter4-Arguments.tex
Fix some typos and reshap LDAMSR diagram

Unfortunately, the proposal they share is indeed problematic. The ghost user proposal prides itself on not compromising
strong encryption. This is a good property, but compromising a messaging app's authorization protocol is as dangerous as
compromising its encryption \cite{callas_1_2019}. Fundamentally, it suffers from the same weakness as trusted-party key
escrow; the introduction of an authorization vulnerability in the messaging service provider's platform amounts to a
highly risky centralization of access capability \cite{schneier_ghost_2019}. It has the same nature, if a different
form, as rejected key escrow proposals.

Finally, one \ac{DAR}-specific \ac{EA} class is device key escrow. In this scheme, key recovery material exists on the
device itself. While not necessary to classify as device key escrow, most of these proposals include physical possession
requirements and additionally ``brick'' the device or make it absolutely clear that \ac{EA} has been performed
\cite{savage_lawful_2018} \cite{ozzie_2018}. Such features precludes mass surveillance and ensure transparency to the
device user. This approach relies on secure hardware and a method of authorizing the recovery request to the device
itself. The authentication step can be paired with other \ac{EA} strategies, such as engaging with trusted-parties or
distributed systems. This is where the device escrow shows its weaknesses. Secure hardware enclaves, though improving,
are not totally reliable, and authentication to the hardware device is susceptible to the same attacks as traditional
escrow \ac{EA}.

Device key escrow's greatest weaknesses, however, still represent signs of progress. It is true that it relies on a
device's secure enclave, but devices already do---it is the same hardware devices that manages device unlock and
encryption functionality in the first place. Adding functionality increases the attack surface, but it does not add a
completely new threat vector. It is also true that the process is subject to the same problems as traditional key escrow
after the device has been obtained, but that is precisely the progress that has been made---\ii{after the device has
been obtained}. Leveraging advances in secure hardware design has meaningfully changed the \ac{EA} risk profile.

>>>>

Unfortunately, the proposal they share is indeed problematic. The ghost user proposal prides itself on not compromising
strong encryption. This is a good property, but compromising a messaging app's authorization protocol is as dangerous as
compromising its encryption \cite{callas_1_2019}. Fundamentally, it suffers from the same weakness as trusted-party key
escrow; the introduction of an authorization vulnerability in the messaging service provider's platform amounts to a
highly risky centralized access capability \cite{schneier_ghost_2019}. It has the same nature, if a different form, as
rejected key escrow proposals.

Finally, one \ac{DAR}-specific \ac{EA} class is device key escrow. In this scheme, key recovery material exists on the
device itself. While not necessary to classify as device key escrow, most of these proposals include physical possession
requirements and additionally ``brick'' the device or make it absolutely clear that \ac{EA} has been performed
\cite{savage_lawful_2018} \cite{ozzie_2018}. Such features preclude mass surveillance and ensure transparency to the
device user. This approach relies on secure hardware and a method of authorizing the recovery request to the device
itself. The authentication step can be paired with other \ac{EA} strategies, such as engaging with trusted-parties or
distributed systems. This is where the device escrow shows its weaknesses. Secure hardware enclaves, though improving,
are not totally reliable, and authentication to the hardware device is susceptible to the same attacks as traditional
escrow \ac{EA}.

Device key escrow's greatest weaknesses, however, still represent signs of progress. It is true that it relies on a
device's secure enclave, but devices already do---it is the same hardware device that manages device unlock and
encryption functionality in the first place. Adding functionality increases the attack surface, but it does not add a
completely new threat vector. It is also true that the process is subject to the same problems as traditional key escrow
after the device has been obtained, but that is precisely the progress that has been made---\ii{after the device has
been obtained}. Leveraging advances in secure hardware design has meaningfully changed the \ac{EA} risk profile.

### 2020-11-07 Thesis-Chapter5-ThreatModel.tex
Finish Chapter 3 draft
Clean up arguments chapter notes
Prepare chapter 5 and start rearranging LDAWMSR diagram
Fix some typos and reshap LDAMSR diagram

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption[A DAR EA Proposal]{A DAR EA Proposal based on \cite{savage_lawful_2018}.}
    \label{fig-dfd-lawful}
\end{figure}

@@

% Generalize for DAR and DIM, then apply to specific examples. This proves that my analysis is helpful. Ex: apply to email: is a DIM _and_ DAR problem due to the server.

%%%%%%%%%%%%
% Chapter 4, threat models
% (how to be specific enough to be useful but generic enough to apply to many systems? Focus on the EA type (DAR v DIM),
%   then apply to specific systems)
% DAR, DIM threat models (make sure to cover abelson_2015)
% Basic proposals
%  --> mappings onto threat models
% At work: 3 example systems analyzed with this threat model
% 1. IM (E2E IM too?) -- in motion
% 2. Cloud storage -- at rest
% 3. Mobile phone -- at rest, but way different scenario than cloud
%  --> include Ozzie's CLEAR, since it was higher profile
%%%%%%%%%%%%

>>>>

\section{Developing a Threat Model}

% For a wholistic threat model, include both the threats of government (legislation) and of criminal abusers of your
% system.

@@

\section{Basic Data at Rest}

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone.png}
    \caption{The basic encrypted mobile phone data flow diagram.}
    \label{fig-dfd-dar}
\end{figure}

\section{The LDAWMSR Proposal}

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=0.81\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption{The LDAWMSR data flow diagram.}
    \label{fig-dfd-ldawmsr}
\end{figure}

\section{Discussion of Threats}

%%%%%%%%%%%%
% Old notes for reference
% -----------------------
% Chapter 4, threat models
% (how to be specific enough to be useful but generic enough to apply to many systems? Focus on the EA type (DAR v DIM),
%   then apply to specific systems)
% DAR, DIM threat models (make sure to cover abelson_2015)
% Basic proposals
%  --> mappings onto threat models
% At work: 3 example systems analyzed with this threat model
% 1. IM (E2E IM too?) -- in motion
% 2. Cloud storage -- at rest
% 3. Mobile phone -- at rest, but way different scenario than cloud
%  --> include Ozzie's CLEAR, since it was higher profile
%%%%%%%%%%%%
